\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-16 paper/related.tex
quick citation fix

Houmansadr et al.~\cite{cirripede11} found that placing refraction proxies in a handful of Tier 1 networks would be sufficient for them to be usable by the majority of the Internet population. Cesareo et al.~\cite{decoy-placement} developed an algorithm for optimizing the placement of proxies based on AS-level Internet topology data. Schuchard et al.~\cite{rad} suggested that a censor may actively change its routes to ensure traffic leaving its country avoids the proxies, but Houmansadr et al.~\cite{true-cost-rad} suggested that real-world constraints on routing make this attack difficult to carry out in practice. Nevertheless, Nasr et al.~\cite{game-of-decoys} propose a game-theoretic framework to optimize proxy placement in an adversarial setting, and the design of Waterfall~\cite{waterfall17} is in part motivated by resilience to routing attacks, as it is more difficult for the censor to control the return path from a decoy site, rather than the forward path.

>>>>

Houmansadr et al.~\cite{cirripede11} found that placing refraction proxies in a 
handful of Tier 1 networks would be sufficient for them to be usable by the 
majority of the Internet population. Cesareo et al.~\cite{decoy-placement} 
developed an algorithm for optimizing the placement of proxies based on AS-level 
Internet topology data. Schuchard et al.~\cite{rad12} suggested that a censor may 
actively change its routes to ensure traffic leaving its country avoids the 
proxies, but Houmansadr et al.~\cite{true-cost-rad} suggested that real-world 
constraints on routing make this attack difficult to carry out in practice. 
Nevertheless, Nasr et al.~\cite{game-of-decoys} propose a game-theoretic 
framework to optimize proxy placement in an adversarial setting, and the 
design of Waterfall~\cite{waterfall17} is in part motivated by resilience to 
routing attacks, as it is more difficult for the censor to control the return 
path from a decoy site, rather than the forward path.
